Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-27 paper/main.tex
fix sec 3

\subsubsection{Sampling step.}\label{sec:sampling}
Sampling from $MM(\sigma_0,\theta)$  can be done efficiently given the parameters  $\sigma_0$ and $\theta$, as studied by \citet{IruCalLoz2016permallows}, where the computational complexity is $O(n\log n)$. % and $O(n^2)$.\MANUEL{X respectively? more than 2}
%
At each iteration of UMM, $\sigma_0=\hat\sigma_0$ is the permutation obtained in the previous learning step. The scale $\theta$ controls the variance and expected distance $\Edist$ of the MM, where $D$ is the distance of a random permutation $\sigma\sim MM(\sigma_0, \theta)$ to the location parameter $\sigma_0$. Both variance and expected distance increase monotonically with the value of $\theta$. In particular, $\Edist$ is given by~\cite{gMallows}:
%
\begin{equation}\label{eq:expectation}
\Edist = \frac{n \cdot \exp(-\theta)}{1-\exp(-\theta)} - \sum_{j=1}^{n}  \frac{j\cdot\exp(-j  \theta)}{1-\exp(-j\theta)}
\end{equation}

>>>>

\subsubsection{Sampling step.}\label{sec:sampling}
Sampling from $MM(\sigma_0,\theta)$  can be done efficiently given the parameters  $\sigma_0$ and $\theta$, as studied by \citet{IruCalLoz2016permallows}, where the computational complexity is $O(n\log n)$. % and $O(n^2)$.\MANUEL{X respectively? more than 2}
%
At each iteration of UMM, $\sigma_0=\hat\sigma_0$ is the permutation obtained in the previous learning step. The scale $\theta$ controls the variance and expected value and variance of the distance $D$ of a random permutation $\sigma\sim MM(\sigma_0, \theta)$ to the location parameter $\sigma_0$. Both  the expected value of $D$ and its variance increase monotonically with the value of $\theta$. In particular, the expected distance $\Edist$ is given by~\cite{gMallows}:
%
\begin{equation}\label{eq:expectation}
\Edist = \frac{n \cdot \exp(-\theta)}{1-\exp(-\theta)} - \sum_{j=1}^{n}  \frac{j\cdot\exp(-j  \theta)}{1-\exp(-j\theta)}
\end{equation}
